---
title: "01_data"
author: "Sglatt"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Github
```{r git, eval=FALSE}
usethis::create_from_github("https://github.com/Sfglatt/smi-mhealth",
  destdir = "~/Github/smi-mhealth"
)
```

# Packages
```{r packages}
if (!require("readxl")) {
  install.packages("readxl")
  require("readxl")
}
if (!require("dplyr")) {
  install.packages("dplyr")
  require("dplyr")
}
if (!require("stringr")) {
  install.packages("stringr")
  require("stringr")
}
if (!require("lubridate")) {
  install.packages("lubridate")
  require("lubridate")
}
```

# Folders for output 
```{r output folders, eval=FALSE}
if (!dir.exists("01_output")) {
  dir.create("01_output")
}

if (!dir.exists("01_output/Individual_merged")) {
  dir.create("01_output/Individual_merged")
}

if (!dir.exists("01_output/All_merged")) {
  dir.create("01_output/All_merged")
}
```

# Convert all raw files to csv
```{r file conversion, eval=FALSE}
# Get all .xlsx files
xlsx_files <- list.files(
  path = "Raw_data",
  pattern = "\\.xlsx$",
  full.names = TRUE
)

xlsx_files

# Loop through files
for (file in xlsx_files) {
  df <- read_excel(file)

  csv_file <- file.path(
    "Raw_data",
    paste0(tools::file_path_sans_ext(basename(file)), ".csv")
  )

  # Save CSV
  write.csv(df, csv_file, row.names = FALSE)
}
```

# Import all csvs
```{r csvs}
csv_files <- list.files(
  path = "Raw_data",
  pattern = "\\.csv$",
  full.names = TRUE
)

for (file in csv_files) {
  obj_name <- tools::file_path_sans_ext(basename(file))
  df <- read.csv(file, stringsAsFactors = FALSE)
  assign(obj_name, df)
}

# Rename the file ALEXIS_004_Frist to ALEXIS_004_First
if (exists("ALEXIS_004_Frist")) {
  assign("ALEXIS_004_First", get("ALEXIS_004_Frist"))
  rm("ALEXIS_004_Frist")
}
```

# Verify that all first, mid, and last surveys have the same column names across participants before looping
```{r protocol}
# First
setdiff(colnames(ALEXIS_001_First), colnames(ALEXIS_002_First))
setdiff(colnames(ALEXIS_002_First), colnames(ALEXIS_001_First))

setdiff(colnames(ALEXIS_001_First), colnames(ALEXIS_004_First))
setdiff(colnames(ALEXIS_004_First), colnames(ALEXIS_001_First))

setdiff(colnames(ALEXIS_001_First), colnames(ALEXIS_005_First))
setdiff(colnames(ALEXIS_005_First), colnames(ALEXIS_001_First))

setdiff(colnames(ALEXIS_001_First), colnames(ALEXIS_006_First))
setdiff(colnames(ALEXIS_006_First), colnames(ALEXIS_001_First))

setdiff(colnames(ALEXIS_001_First), colnames(ALEXIS_007_First))
setdiff(colnames(ALEXIS_007_First), colnames(ALEXIS_001_First))

setdiff(colnames(ALEXIS_001_First), colnames(ALEXIS_008_First))
setdiff(colnames(ALEXIS_008_First), colnames(ALEXIS_001_First))

setdiff(colnames(ALEXIS_001_First), colnames(ALEXIS_009_First))
setdiff(colnames(ALEXIS_009_First), colnames(ALEXIS_001_First))

# Mid
setdiff(colnames(ALEXIS_001_Mid), colnames(ALEXIS_002_Mid))
setdiff(colnames(ALEXIS_002_Mid), colnames(ALEXIS_001_Mid))

setdiff(colnames(ALEXIS_001_Mid), colnames(ALEXIS_004_Mid))
setdiff(colnames(ALEXIS_004_Mid), colnames(ALEXIS_001_Mid))

setdiff(colnames(ALEXIS_001_Mid), colnames(ALEXIS_005_Mid))
setdiff(colnames(ALEXIS_005_Mid), colnames(ALEXIS_001_Mid))

setdiff(colnames(ALEXIS_001_Mid), colnames(ALEXIS_006_Mid))
setdiff(colnames(ALEXIS_006_Mid), colnames(ALEXIS_001_Mid))

setdiff(colnames(ALEXIS_001_Mid), colnames(ALEXIS_007_Mid))
setdiff(colnames(ALEXIS_007_Mid), colnames(ALEXIS_001_Mid))

setdiff(colnames(ALEXIS_001_Mid), colnames(ALEXIS_008_Mid))
setdiff(colnames(ALEXIS_008_Mid), colnames(ALEXIS_001_Mid))

setdiff(colnames(ALEXIS_001_Mid), colnames(ALEXIS_009_Mid))
setdiff(colnames(ALEXIS_009_Mid), colnames(ALEXIS_001_Mid))

# Last
setdiff(colnames(ALEXIS_001_Last), colnames(ALEXIS_002_Last))
setdiff(colnames(ALEXIS_002_Last), colnames(ALEXIS_001_Last))

setdiff(colnames(ALEXIS_001_Last), colnames(ALEXIS_004_Last))
setdiff(colnames(ALEXIS_004_Last), colnames(ALEXIS_001_Last))

setdiff(colnames(ALEXIS_001_Last), colnames(ALEXIS_005_Last))
setdiff(colnames(ALEXIS_005_Last), colnames(ALEXIS_001_Last))

setdiff(colnames(ALEXIS_001_Last), colnames(ALEXIS_006_Last))
setdiff(colnames(ALEXIS_006_Last), colnames(ALEXIS_001_Last))

setdiff(colnames(ALEXIS_001_Last), colnames(ALEXIS_007_Last))
setdiff(colnames(ALEXIS_007_Last), colnames(ALEXIS_001_Last))

setdiff(colnames(ALEXIS_001_Last), colnames(ALEXIS_008_Last))
setdiff(colnames(ALEXIS_008_Last), colnames(ALEXIS_001_Last))

setdiff(colnames(ALEXIS_001_Last), colnames(ALEXIS_009_Last))
setdiff(colnames(ALEXIS_009_Last), colnames(ALEXIS_001_Last))
# Good
```

# Check structure/overlap columns between first/mid/last surveys for one participant
# Then loop the process for the rest of the participants
```{r structure}
colnames(ALEXIS_001_First)
colnames(ALEXIS_001_Mid)
colnames(ALEXIS_001_Last)

# Convert date to POSIXct
ALEXIS_001_First$global_date <- as.POSIXct(
  ALEXIS_001_First$global_date,
  tz = "UTC"
)

ALEXIS_001_Mid$global_date <- as.POSIXct(
  ALEXIS_001_Mid$global_date,
  tz = "UTC"
)

ALEXIS_001_Last$global_date <- as.POSIXct(
  ALEXIS_001_Last$global_date,
  tz = "UTC"
)

# Add a wave label
ALEXIS_001_First$wave <- "first"
ALEXIS_001_Mid$wave <- "mid"
ALEXIS_001_Last$wave <- "last"

ALEXIS_001_First$source_dataset <- paste0("ALEXIS_001_First")
ALEXIS_001_Mid$source_dataset <- paste0("ALEXIS_001_Mid")
ALEXIS_001_Last$source_dataset <- paste0("ALEXIS_001_Last")


ALEXIS_001_combined <- bind_rows(
  ALEXIS_001_First,
  ALEXIS_001_Mid,
  ALEXIS_001_Last
) %>%
  arrange(subject_id, global_date)

# Sort chronologically
ALEXIS_001_combined <- ALEXIS_001_combined %>%
  arrange(global_date) %>%
  select(subject_id, wave, source_dataset, global_date, everything())

# Check for duplicate timestamp and instance key
ALEXIS_001_combined %>%
  count(subject_id, timestamp) %>%
  filter(n > 1) %>%
  arrange(desc(n))

ALEXIS_001_combined %>%
  count(subject_id, instance_key) %>%
  filter(n > 1) %>%
  arrange(desc(n))

any(duplicated(names(ALEXIS_001_combined)))
```

# Merge surveys into one file per person
```{r}
ids <- sprintf("ALEXIS_%03d", c(2, 4:9))
ids

for (id in ids) {
  first_obj <- get(paste0(id, "_First"))
  mid_obj <- get(paste0(id, "_Mid"))
  last_obj <- get(paste0(id, "_Last"))

  # Add wave identifier
  first_obj$wave <- "first"
  mid_obj$wave <- "mid"
  last_obj$wave <- "last"

  first_obj$source_dataset <- paste0(id, "_First")
  mid_obj$source_dataset <- paste0(id, "_Mid")
  last_obj$source_dataset <- paste0(id, "_Last")

  # Convert dates
  first_obj$global_date <- as.POSIXct(first_obj$global_date, tz = "UTC")
  mid_obj$global_date <- as.POSIXct(mid_obj$global_date, tz = "UTC")
  last_obj$global_date <- as.POSIXct(last_obj$global_date, tz = "UTC")

  # Combine
  combined <- bind_rows(first_obj, mid_obj, last_obj) %>%
    arrange(subject_id, global_date, source_dataset, wave, instance_key)

  print(
    combined %>%
      count(subject_id, timestamp) %>%
      filter(n > 1)
  )

  print(
    combined %>%
      count(subject_id, instance_key) %>%
      filter(n > 1)
  )

  # Save back into global environment
  assign(paste0(id, "_combined"), combined)
}
```

# Save the individual combined files
```{r save individual combined}
ids <- sprintf("ALEXIS_%03d", c(1:2, 4:9))
ids

for (id in ids) {
  obj_name <- paste0(id, "_combined")

  if (exists(obj_name)) {
    df <- get(obj_name)

    write.csv(
      df,
      file.path(
        "01_output/Individual_merged",
        paste0(id, "_sg_", format(Sys.Date(), "%Y-%m-%d"), ".csv")
      ),
      row.names = FALSE
    )
  }
}
```

# Merge all individual combined files together for one master file
```{r merge all}
# Make sure all combined files are the same
list(
  only_in_001 = setdiff(names(ALEXIS_001_combined), names(ALEXIS_002_combined)),
  only_in_002 = setdiff(names(ALEXIS_002_combined), names(ALEXIS_001_combined))
)

# 002
list(
  "ALEXIS_002_only_in_001" = setdiff(names(ALEXIS_001_combined), names(ALEXIS_002_combined)),
  "ALEXIS_002_only_in_002" = setdiff(names(ALEXIS_002_combined), names(ALEXIS_001_combined))
)

# 004
list(
  "ALEXIS_004_only_in_001" = setdiff(names(ALEXIS_001_combined), names(ALEXIS_004_combined)),
  "ALEXIS_004_only_in_004" = setdiff(names(ALEXIS_004_combined), names(ALEXIS_001_combined))
)

# 005
list(
  "ALEXIS_005_only_in_001" = setdiff(names(ALEXIS_001_combined), names(ALEXIS_005_combined)),
  "ALEXIS_005_only_in_005" = setdiff(names(ALEXIS_005_combined), names(ALEXIS_001_combined))
)

# 006
list(
  "ALEXIS_006_only_in_001" = setdiff(names(ALEXIS_001_combined), names(ALEXIS_006_combined)),
  "ALEXIS_006_only_in_006" = setdiff(names(ALEXIS_006_combined), names(ALEXIS_001_combined))
)

# 007
list(
  "ALEXIS_007_only_in_001" = setdiff(names(ALEXIS_001_combined), names(ALEXIS_007_combined)),
  "ALEXIS_007_only_in_007" = setdiff(names(ALEXIS_007_combined), names(ALEXIS_001_combined))
)

# 008
list(
  "ALEXIS_008_only_in_001" = setdiff(names(ALEXIS_001_combined), names(ALEXIS_008_combined)),
  "ALEXIS_008_only_in_008" = setdiff(names(ALEXIS_008_combined), names(ALEXIS_001_combined))
)

# 009
list(
  "ALEXIS_009_only_in_001" = setdiff(names(ALEXIS_001_combined), names(ALEXIS_009_combined)),
  "ALEXIS_009_only_in_009" = setdiff(names(ALEXIS_009_combined), names(ALEXIS_001_combined))
)

identical(
  names(ALEXIS_001_combined),
  names(ALEXIS_002_combined)
)

# Merge all
ALEXIS_all_combined <- bind_rows(
  ALEXIS_001_combined,
  ALEXIS_002_combined,
  ALEXIS_004_combined,
  ALEXIS_005_combined,
  ALEXIS_006_combined,
  ALEXIS_007_combined,
  ALEXIS_008_combined,
  ALEXIS_009_combined
) %>%
  arrange(subject_id, global_date)

# Check for duplicate timestamp and instance key within subject id
ALEXIS_all_combined %>%
  count(subject_id, timestamp, wave, instance_key) %>%
  filter(n > 1) %>%
  arrange(desc(n))

ALEXIS_all_combined %>%
  filter(subject_id == 67334) %>%
  arrange(timestamp) %>%
  select(subject_id, timestamp, instance_key, source_dataset, wave)

# ALEXIS_007 and ALEXIS_008 have the *same* subject ID, timestamp, and instance key for some observatios
# Look at subject IDs in 007 and 008
table(ALEXIS_007_combined$subject_id)
table(ALEXIS_008_combined$subject_id)

# The error is with 007
# look at their individual surveys to see if the subject ID is consistent across all three waves
table(ALEXIS_007_Mid$subject_id) # Consistent
table(ALEXIS_007_Last$subject_id) # Consistent
table(ALEXIS_007_First$subject_id) # Not consistent - 67334 (the same as 008) in first, but 67333 in mid and last

# Check if they are duplicates
head(ALEXIS_007_First)
head(ALEXIS_008_First)

# Re-merge without 007 for now
# Merge all
ALEXIS_all_combined_x007 <- bind_rows(
  ALEXIS_001_combined,
  ALEXIS_002_combined,
  ALEXIS_004_combined,
  ALEXIS_005_combined,
  ALEXIS_006_combined,
  ALEXIS_008_combined,
  ALEXIS_009_combined
) %>%
  arrange(subject_id, global_date)

# Check for duplicate timestamp and instance key within subject id
ALEXIS_all_combined_x007 %>%
  count(subject_id, timestamp, wave, instance_key) %>%
  filter(n > 1) %>%
  arrange(desc(n))
# Good
```

# Filter to just the EMA surveys (mid)
```{r filter mid}
ALEXIS_all_mid_x007 <- ALEXIS_all_combined_x007 %>% 
  filter(wave == "mid") %>%
  arrange(subject_id, global_date)
```

# Add a day and beep variable
```{r da/beep vars}
ALEXIS_all_mid_x007 <- ALEXIS_all_mid_x007 %>%
  group_by(subject_id) %>%
  arrange(global_date, .by_group = TRUE) %>%
  mutate(
    day = as.integer(as.Date(global_date) - as.Date(min(global_date))) + 1,
    beep = row_number()
  ) %>%
  ungroup()
```

# Save the combined (without 007 for now) files
```{r save combined}
# First/mid/last combined
write.csv(ALEXIS_all_combined_x007,
  file = paste0("01_output/All_merged/ALEXIS_all_merged_sg_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)

# The mid EMA surveys with day/beep
write.csv(ALEXIS_all_mid_x007,
  file = paste0("01_output/All_merged/ALEXIS_mid_merged_sg_", format(Sys.Date(), "%Y-%m-%d"), ".csv"),
  row.names = TRUE
)
```

